Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]

### 2013-09-18 snapshot_system/fast14_evaluation.tex
change to table

\begin{figure}
    \centering
    \subfigure[Backup throughput per node under controlled I/O bandwidth usage]
    {
        \includegraphics[width=3in]{figures/parallel_backup_with_read}
        \label{fig:withread}
    }
    \\
    \subfigure[Deduplication and storage system performance]
    {
        \includegraphics[width=3in]{figures/parallel_backup_no_read}
        \label{fig:noread}
    }
    \caption{Throughput per-node with concurrent snapshot backup tasks}
    \label{fig:parallel_backup}
\end{figure}

\subsection{Effectiveness of Approximate Deletion}
\begin{figure}
    \centering
    \includegraphics[width=3in]{figures/leakage}
    \caption{Accumulated storage leakage by approximate snapshot deletions}
    \label{fig:leakage}
\end{figure}

>>>>

\begin{table}
    \begin{tabular}{l|lll|lll}
    Num. of concurrent      & \multicolumn{2}{l}{Throughput without I/O throttling (MB/s)} & \multicolumn{2}{l}{Throughput with I/O throttling (MB/s)} \\
    backup streams per node & Raw                                       & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\
    1                       & 1369.6                                    & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
    2                       & 2408.5                                    & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
    4                       & 4101.8                                    & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
    6                       & 5456.5                                    & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
    \end{tabular}
\end{table}

% \begin{figure}
%     \centering
%     \subfigure[Backup throughput per node under controlled I/O bandwidth usage]
%     {
%         \includegraphics[width=3in]{figures/parallel_backup_with_read}
%         \label{fig:withread}
%     }
%     \\
%     \subfigure[Deduplication and storage system performance]
%     {
%         \includegraphics[width=3in]{figures/parallel_backup_no_read}
%         \label{fig:noread}
%     }
%     \caption{Throughput per-node with concurrent snapshot backup tasks}
%     \label{fig:parallel_backup}
% \end{figure}

% \subsection{Effectiveness of Approximate Deletion}
% \begin{figure}
%     \centering
%     \includegraphics[width=3in]{figures/leakage}
%     \caption{Accumulated storage leakage by approximate snapshot deletions}
%     \label{fig:leakage}
% \end{figure}
